Alternative Methods for Retaining Explicit and Finding Implicit Sharing in Embedded DSLs

### 2023-02-15 paper/paper.tex
small update to introduction

In the toy example
\begin{minted}{haskell}
class Exp repr where
  variable :: String -> repr Int
  constant :: String -> repr Int
  add :: repr Int -> repr Int -> repr Int
  novel :: (repr Int,repr Int) -> (repr Int,repr Int)
\end{minted}
the function \mintinline{haskell}{novel} will exhibit this issue. Since it
returns multiple outputs via a native tuple or list, it will cause duplication
of computation that cannot be captured by Kiselyov's explicit sharing
method. We will illustrate this implementation issue in Section
\ref{limitexplicit}. In our work, this translated into the inability to process
large library functions.

>>>>

In the toy example
\begin{minted}{haskell}
class Exp repr where
  variable :: String -> repr Int
  constant :: String -> repr Int
  add :: repr Int -> repr Int -> repr Int
  novel :: (repr Int,repr Int) -> (repr Int,repr Int)
\end{minted}
the function \mintinline{haskell}{novel} will exhibit this issue. Since it
returns multiple outputs via a native tuple or list, it will cause duplication
of computation that cannot be captured by Kiselyov's explicit sharing method. We
will illustrate this implementation issue in Section \ref{limitexplicit}.
Encountering this issue in our own work with eDSLs for code generation caused a
computational explosion on large DAGs.
